---
title: 'Frequentist Data Analysis Code for the Many Smiles Collaboration'
editor_options:
  chunk_output_type: console
---
## Notes for Marco
When I tested the code with 10 iterations, the following models yielded "NA" for the Bayes Factors (a) the Pose by Condition interaction models, and (b) the simple effect models. I could override this by adding "noSample = F" as an argument--but I left that code out for now in case the error message was actually driven by problems with the small number of iterations I specified. 

## Setup R environment
```{r message = FALSE, results = "hide"}
# clear environment
rm(list = ls())

# set seed
set.seed(2)

# turn scientific notation off
options(scipen = 999)

# allow for Type III Sums of Square
options(contrasts = c('contr.sum', 'contr.poly'))


# install (if necessary) and load packages
  # function written by stevenworthington 
  Ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, 'Package'])]
      
      if (length(new.pkg)) 
          install.packages(new.pkg, dependencies = TRUE)
      
      sapply(pkg, require, character.only = TRUE)
  }

  # vector of necessary packages
  packages <- c('tidyverse', 'BayesFactor')
  
  # using vector of packages, call ipak function
  Ipak(packages)
  
  # delete vestigial
  rm(packages, Ipak)
```

## Open data
```{r}
DF.l.inc <- readRDS("data/processed/DF.l.inc.rds") %>% 
  mutate(ResponseId = ResponseId %>% 
           as.numeric() %>% 
           as.factor()
         ) %>% 
  as.data.frame()

DF.l <- readRDS("data/processed/DF.l.rds") %>% 
  mutate(ResponseId = ResponseId %>% 
           as.numeric() %>% 
           as.factor()
         ) %>% 
  as.data.frame()
```

## Set prior and iterations
User should select whichever prior they wish to test (medium, wide, or ultrawide)
```{r}
pr <- "medium"
#pr <- "wide"
#pr <- "ultrawide"
```

Iterations should be set to 1000 by default, but users can adjust as needed
```{r}
it <- 1000
```

## Primary analyses
### With random slopes
#### Pose main effect
```{r}
p.1 <- 
  lmBF(happiness ~ trial +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)


p.0 <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"), 
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

p <- p.1 / p.0
```

#### Condition main effect
```{r}
c.1 <- 
  lmBF(happiness ~ condition +
         ResponseId + lab + lab:condition, 
       whichRandom = c("ResponseId", "lab", "lab:condition"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

c.0 <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab : condition, 
       whichRandom = c("ResponseId", "lab", "lab:condition"), 
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

c <- c.1 / c.1
```

#### Image main effect
```{r}
i.1 <- 
  lmBF(happiness ~ image +
         ResponseId + lab + lab:image, 
       whichRandom = c("ResponseId", "lab", "lab:image"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

i.0 <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab:image, 
       whichRandom = c("ResponseId", "lab", "lab:image"), 
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

i <- i.1 / i.0
```

#### Pose by condition interaction
```{r}
pc.1 <- 
  lmBF(happiness ~ trial + condition + trial:condition +
         ResponseId + lab + lab:trial + lab:condition + lab:trial:condition,
       whichRandom = c("ResponseId", "lab", 
                       "lab:trial", "lab:condition",
                       "lab:trial:condition"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

pc.0 <- 
  lmBF(happiness ~ trial + condition +
         ResponseId + lab + lab:trial + lab:condition + lab:trial:condition, 
       whichRandom = c("ResponseId", "lab", 
                       "lab:trial", "lab:condition",
                       "lab:trial:condition"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

pc <- pc.1 / pc.0
```

#### Pose simple effects
Facial mimicry
```{r}
p.1.m <- 
  lmBF(happiness ~ trial +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"),
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "mimicry"),
       iterations = it)


p.0.m <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"), 
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "mimicry"),
       iterations = it)

p.m <- p.1.m / p.0.m
```

Voluntary facial action task
```{r}
p.1.v <- 
  lmBF(happiness ~ trial +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"),
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "directd"),
       iterations = it)


p.0.v <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab:trial,
       whichRandom = c("ResponseId", "lab", "lab:trial"), 
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "directd"),
       iterations = it)

p.v <- p.1.v / p.0.v
```

Pen-in-mouth
```{r}
p.1.p <- 
  lmBF(happiness ~ trial +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"),
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "pentask"),
       iterations = it)


p.0.p <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab + lab:trial, 
       whichRandom = c("ResponseId", "lab", "lab:trial"), 
       rscaleFixed = pr,
       data = subset(DF.l.inc, 
                     condition == "pentask"),
       iterations = it)

p.p <- p.1.p / p.0.p
```

## Exploratory analyses
### Pose by image interaction w/out random slopes
```{r}
exp.pi.1 <- 
  lmBF(happiness ~ trial + image + trial:image +
         ResponseId + lab,  
       whichRandom = c("ResponseId", "lab"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)


exp.pi.0 <- 
  lmBF(happiness ~ trial + image +
         ResponseId + lab,  
       whichRandom = c("ResponseId", "lab"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

exp.pi <- exp.pi.1 / exp.pi.0
```

### Pose by condition by image interaction w/out random slopes
```{r}
exp.pci.1 <- 
  lmBF(happiness ~ trial + condition + image + 
         trial:condition + trial:image + trial:condition +
         trial:condition:image +
         ResponseId + lab, 
       whichRandom = c("ResponseId", "lab"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)


exp.pci.0 <- 
  lmBF(happiness ~ trial + condition + image + 
         trial:condition + trial:image + trial:condition +
         ResponseId + lab, 
       whichRandom = c("ResponseId", "lab"),
       rscaleFixed = pr,
       data = DF.l.inc,
       iterations = it)

exp.pci <- exp.pci.1 / exp.pci.0
```

### Pen-in-mouth effect w/out random slopes  or  exclusions
```{r}
exp.p.1.p <- 
  lmBF(happiness ~ trial +
         ResponseId + lab, 
       whichRandom = c("ResponseId", "lab"),
       rscaleFixed = pr,
       data = subset(DF.l, 
                     condition == "pentask"),
       iterations = it)

exp.p.0.p <- 
  lmBF(happiness ~ 1 +
         ResponseId + lab, 
       whichRandom = c("ResponseId", "lab"), 
       rscaleFixed = pr,
       data = subset(DF.l, 
                     condition == "pentask"),
       iterations = it)

exp.p.p <- exp.p.1.p / exp.p.0.p
```


## Save models
```{r}
bayes.models <-
  list(p.1 = p.1,
       p.0 = p.0,
       c.1 = c.1,
       c.0 = c.0,
       i.1 = i.1,
       i.0 = i.0,
       pc.1 = pc.1,
       pc.0 = pc.0,
       p.1.m = p.1.m,
       p.0.m = p.0.m,
       p.1.v = p.1.v,
       p.0.v = p.0.v,
       p.1.p = p.1.p,
       p.0.p = p.0.p,
       exp.pi.1 = exp.pi.1,
       exp.pi.0 = exp.pi.0,
       exp.pci.1 = exp.pci.1,
       exp.pci.0 = exp.pci.0,
       exp.p.1.p = exp.p.1.p,
       exp.p.0.p = exp.p.0.p)

saveRDS(bayes.models, 
        file = paste0(#"output/analyses/", # commented out for now
                      "bayes.models.",
                      pr,
                      ".Rds")
        )
```

## Save output
```{r}
output <- 
  c(p@bayesFactor$bf, 
    c@bayesFactor$bf, 
    i@bayesFactor$bf, 
    pc@bayesFactor$bf, 
    p.m@bayesFactor$bf, 
    p.v@bayesFactor$bf, 
    p.p@bayesFactor$bf, 
    exp.pi@bayesFactor$bf, 
    exp.pci@bayesFactor$bf,
    exp.p.p@bayesFactor$bf)

write.table(t(round(exp(output), 2)),
            file = paste0(#"output/analyses/", # commented out for now
                          "BayesFactor.",
                          pr,
                          ".txt"),
            quote = F,
            col.names = F,
            row.names = F,
            append = T)
```

## Optional [save image]
```{r}
save.image(paste0("BayesFactorAnalyses",
                  pr,
                  ".RData")
           )
```

