---
title: 'Data Analysis Code for the Many Smiles Collaboration'
editor_options:
  chunk_output_type: console
---
## Setup R environment
```{r message = FALSE, results = "hide"}
# clear environment
rm(list = ls())

# install (if necessary) and load packages
  # function written by stevenworthington 
  Ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, 'Package'])]
      
      if (length(new.pkg)) 
          install.packages(new.pkg, dependencies = TRUE)
      
      sapply(pkg, require, character.only = TRUE)
  }

  # vector of necessary packages
  packages <- c('tidyverse', 'ggplot2', 'lme4',
                'lmerTest', 'emmeans', 'metafor',
                'ggtext')
  
  # using vector of packages, call ipak function
  Ipak(packages)
  
  # delete vestigial
  rm(packages, Ipak)

# turn scientific notation off
options(scipen = 999)

# allow for Type III Sums of Square
options(contrasts = c('contr.sum', 'contr.poly'))

# set plotting options 
theme_set(theme_classic() +
          theme(strip.background = element_rect(fill = "gray35"),
                strip.text =element_text(colour = "white"),
                panel.border = element_blank(),
                legend.position = "none"
                )
          )
```

## Open data
```{r}
DF.w <- readRDS("data/processed/DF.w.rds")
DF.l.full <- readRDS("data/processed/DF.l.full.rds")
DF.l.full.inc <- readRDS("data/processed/DF.l.full.inc.rds")
DF.l <- readRDS("data/processed/DF.l.rds")
DF.l.inc <- readRDS("data/processed/DF.l.inc.rds")
```

## Descriptives table
```{r}
# descriptives for full sample 
desc.1 <- DF.w %>% 
  group_by(country) %>% 
  summarise(t.n = n(),
            t.m.age = mean(indiv_agee_var,
                         na.rm = T),
            t.sd.age = sd(indiv_agee_var,
                        na.rm = T),
            t.women = sum(indiv_gend_var == 1, na.rm = T) / n(),
            t.men = sum(indiv_gend_var == 2, na.rm = T) / n(),
            t.other = sum(indiv_gend_var == 3, na.rm = T) / n(),
            
            # inclusion criteria pass rate
            inc.att = mean(inc.att),
            inc.fol = mean(inc.fol),
            inc.mat = mean(inc.mat),
            inc.dev = mean(inc.dev),
            inc.awa = sum(inc.awa, na.rm = T) / n(),
            inc.dis = sum(inc.dis, na.rm = T) / n()
            )

# descriptives for subset that met inclusion criteria 
desc.2 <- DF.w %>% 
  filter(inc == 1,
         inc.awa == 1) %>% 
  group_by(country) %>% 
  summarise(i.n = n(),
            i.m.age = mean(indiv_agee_var,
                         na.rm = T),
            i.sd.age = sd(indiv_agee_var,
                        na.rm = T),
            i.women = sum(indiv_gend_var == 1, na.rm = T) / n(),
            i.men = sum(indiv_gend_var == 2, na.rm = T) / n(),
            i.other = sum(indiv_gend_var == 3, na.rm = T) / n()
            )

# merge descriptives
desc = full_join(desc.1, desc.2, by = 'country')
rm(desc.1, desc.2)

# clean table
desc <- desc %>% 
  # round values
  mutate_if(is.numeric,
            funs(round(x = .,
                       digits = 2)
                  )
            ) %>% 
  
  # create age text
  mutate(t.m.age = paste0(t.m.age, 
                          " (", t.sd.age, ")"),
         i.m.age = paste0(i.m.age,
                          " (", i.m.age, ")")
         ) %>% 
  
  # create gender text
  mutate(t.women = paste0(t.women, "; ",
                          t.men, "; ",
                          t.other),
         i.women = paste0(i.women, "; ",
                          i.men, "; ",
                          i.other)) %>% 

  # delete vestigial
  select(-c(t.sd.age, t.men, t.other, 
            i.sd.age, i.men, i.other))

# export table
write.csv(desc, "desc.csv")
```


## Participant descriptives
```{r}
# n participants
DF.w %>% nrow()

# n labs
DF.l$lab %>% unique() %>% length()

# n countries
DF.l$lab %>% 
  substr(start = 1,
         stop = 3) %>% 
  unique() %>% 
  length()

# condition n
table(DF.l$condition) %>% prop.table()
table(DF.l$condition, DF.l$image) %>% prop.table()

# inclusion criteria
DF.w %>%
  summarise(n = n(),
            m.age = mean(indiv_agee_var,
                         na.rm = T),
            sd.age = sd(indiv_agee_var,
                        na.rm = T),
            g.women = sum(indiv_gend_var == 1, na.rm = T) / n(),
            g.men = sum(indiv_gend_var == 2, na.rm = T) / n(),
            g.other = sum(indiv_gend_var == 3, na.rm = T) / n(),
            
            # inclusion criteria pass rate
            inc.dev = mean(inc.dev),
            inc.att = mean(inc.att),
            inc.fol = mean(inc.fol),
            inc.mat = mean(inc.mat),
            inc.dis = sum(inc.dis, na.rm = T) / n(),
            inc.awa = sum(inc.awa, na.rm = T) / n()
            )
```

## Analyses
Create list to save models in
```{r}
models <- list()
```

### Primary analyses
#### With application of pre-registered exclusion criteria
Fit model and inspect results
```{r}
# fit model 
models[["primary"]][["prereg.min"]] <-
  lmer(happiness ~ trial * condition * image +
         (1 | ResponseId) +
         (1 | lab),
       data = DF.l.inc)

# inspect results
summary(models[["primary"]][["prereg.min"]])

anova(models[["primary"]][["prereg.min"]])

joint_tests(models[["primary"]][["prereg.min"]],
            by = "condition",
            lmerTest.limit = 9999)

joint_tests(models[["primary"]][["prereg.min"]], 
            by = c("image", "condition"),
            lmerTest.limit = 9999)

# descriptives
emmeans(models[["primary"]][["prereg.min"]],
        pairwise ~ image | condition,
        adjust = "none")

emmeans(models[["primary"]][["prereg.min"]],
        pairwise ~ trial | condition,
        adjust = "none")

emmeans(models[["primary"]][["prereg.min"]],
        pairwise ~ trial | image |condition,
        adjust = "none")
```

Simple comparison of facial mimicry and voluntary facial action task
```{r}
lmer(happiness ~ trial * condition * image +
       (1 | ResponseId) +
       (1 | lab),
     data = DF.l.inc,
     subset = condition != "pentask") %>% 
  anova()
```

#### Sensitivity analysis with maximal model
Note: this code is all set to not evaluate because it is computationally intensive

Fit model and inspect results
```{r eval = F}
# fit model
models[["primary"]][["prereg.max"]] <-
  lmer(happiness ~ trial * condition * image +
         (1 | ResponseId) +
         (1 + trial * condition * image | lab),
       data = DF.l.inc)

# inspect results
summary(models[["primary"]][["prereg.max"]])

anova(models[["primary"]][["prereg.max"]])

joint_tests(models[["primary"]][["prereg.max"]],
            by = "condition",
            lmerTest.limit = 9999)

joint_tests(models[["primary"]][["prereg.max"]], 
            by = c("image", "condition"),
            lmerTest.limit = 9999)

# descriptives
emmeans(models[["primary"]][["prereg.max"]],
        pairwise ~ trial | condition,
        adjust = "none")

emmeans(models[["primary"]][["prereg.max"]],
        pairwise ~ trial | image | condition,
        adjust = "none")
```

#### Sensitivity analysis with full dataset
Fit model and inspect results
```{r}
# fit model
models[["primary"]][["full.sens"]] <-
  lmer(happiness ~ trial * condition * image +
         (1 | ResponseId) +
         (1 | lab),
       data = DF.l)

# inspect results
summary(models[["primary"]][["full.sens"]])

anova(models[["primary"]][["full.sens"]])

joint_tests(models[["primary"]][["full.sens"]], 
            by = "condition",
            lmerTest.limit = 9999)

emmeans(models[["primary"]][["full.sens"]],
        pairwise ~ trial | condition,
        adjust = "none")

joint_tests(models[["primary"]][["full.sens"]], 
            by = c("image", "condition"),
            lmerTest.limit = 9999)
```

### Secondary analyses
#### Do Participants Report Experiencing More Happiness During the Smiling vs. Filler Trials?
Fit model and inspect results
```{r}
# fit model
models[["secondary"]][["alt.exp"]] <-
  lmer(happiness ~ trial * condition * image +
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l.full.inc)

# inspect results
anova(models[["secondary"]][["alt.exp"]])

joint_tests(models[["secondary"]][["alt.exp"]], 
            by = "image",
            lmerTest.limit = 9999)

emmeans(models[["secondary"]][["alt.exp"]], 
        pairwise ~ trial | condition | image,
        adjust = "none")
```

##### Sensitivity analysis without exclusions
Fit model and inspect results
```{r}
# fit model
models[["secondary"]][["alt.exp.no.inc"]] <-
  lmer(happiness ~ trial * condition * image +
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l.full)

# inspect results
anova(models[["secondary"]][["alt.exp.no.inc"]])

joint_tests(models[["secondary"]][["alt.exp.no.inc"]], 
            by = "image",
            lmerTest.limit = 9999)

emmeans(models[["secondary"]][["alt.exp.no.inc"]], 
        pairwise ~ trial | condition | image,
        adjust = "none")
```

##### Sensitivity analysis with maximial model
Note: this code is all set to not evaluate because it is computationally intensive. It also removes the image absent condition because (a) it helps the model converge in a reasonably quick amount of time and (b) this condition is not relevant for the inferences (see manuscript for more information).  
```{r eval = F}
# prepare data
tmp <- DF.l.full.inc %>% 
  filter(image == "absentt")

# fit model
models[["secondary"]][["alt.exp"]] <-
  lmer(happiness ~ trial * condition +
         (1 + trial * condition | lab) +
         (1 | ResponseId),
       data = tmp)

# inspect results
anova(models[["secondary"]][["alt.exp"]])

emmeans(models[["secondary"]][["alt.exp"]], 
        pairwise ~ trial | condition,
        adjust = "none")

rm(tmp)
```

#### Effect of facial feedback on anxiety and anger
Anxiety: fit model and inspect results
```{r}
# fit model
models[["secondary"]][["anxiety"]] <-
  lmer(anxiety ~ trial * image * condition + 
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l)

# inspect results
anova(models[["secondary"]][["anxiety"]])
```

Anger: fit model and inspect results
```{r}
# fit model
models[["secondary"]][["anger"]] <-
  lmer(anger ~ trial * image * condition + 
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l)

# inspect results
anova(models[["secondary"]][["anger"]])
```

Descriptives
```{r}
DF.l %>% 
  group_by(condition) %>% 
  summarise(m.anx = mean(anxiety),
            sd.anx = sd(anxiety),
            m.ang = mean(anger),
            sd.ang = sd(anger))

DF.l %>% 
  group_by(trial) %>% 
  summarise(m.anx = mean(anxiety),
            sd.anx = sd(anxiety),
            m.ang = mean(anger),
            sd.ang = sd(anger))
```

#### Moderator analyses
##### Quality
###### Compliance with instructions
```{r}
# fit model
models[["secondary"]][["quality.rating"]] <-
  lmer(happiness ~ 
         trial * condition * image * qulty_rate_var.c +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# inspect results
anova(models[["secondary"]][["quality.rating"]])
```

Look at facial feedback task-specific moderating effects
```{r}
# mimicry
m <- lmer(happiness ~ 
            trial * image * qulty_rate_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "mimicry")

m %>% anova()
m %>% summary()
m %>% confint()

# voluntary facial action task
m <- lmer(happiness ~ 
            trial * image * qulty_rate_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "directd")

m %>% anova()
m %>% summary()
m %>% confint()

# pen-in-mouth
m <- lmer(happiness ~ 
            trial * image * qulty_rate_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "pentask") 

m %>% anova()
m %>% summary()
m %>% confint()

rm(m)
```

Examine how much adherence is required for a significant facial feedback effect
```{r}
# fit simpler model without centered variable for ease of interpretation
tmp <- lmer(happiness ~ 
              trial * condition * qulty_rate_var +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# five is where there is a switch (except for pen, which requires a 6)
lapply(X = c(1 : 7), 
       function(x){
         emmeans(tmp,
                 pairwise ~ trial | condition,
                 at = list(qulty_rate_var = x))
         }
       )

# delete vestigial
rm(tmp)
```

###### Pose similarity
```{r}
# fit model
models[["secondary"]][["simil.rating"]] <-
  lmer(happiness ~ 
         trial * condition * image * qulty_smlr_var.c +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# inspect results
anova(models[["secondary"]][["simil.rating"]])
```

Look at facial feedback task-specific moderating effects
```{r}
# mimicry
m <- lmer(happiness ~ 
            trial * image * qulty_smlr_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "mimicry")

m %>% anova()
m %>% summary()
m %>% confint()

# voluntary facial action task
m <- lmer(happiness ~ 
            trial * image * qulty_smlr_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "directd")

m %>% anova()
m %>% summary()
m %>% confint()

# pen-in-mouth
m <- lmer(happiness ~ 
            trial * image * qulty_smlr_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "pentask")

m %>% anova()
m %>% summary()
m %>% confint()

rm(m)
```

Examine how much similarity is required for a significant facial feedback effect
```{r}
# fit simpler model without centered variable for ease of interpretation
tmp <- lmer(happiness ~ 
              trial * condition * qulty_smlr_var +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# 2 is where there is a switch (for all besides mimicry, which requires a 3)
lapply(X = c(1 : 7), 
       function(x){
         emmeans(tmp,
                 pairwise ~ trial | condition,
                 at = list(qulty_smlr_var = x))
         }
       )

# delete vestigial
rm(tmp)
```

###### Genuineness ratings
```{r}
# fit model
models[["secondary"]][["feel.rating"]] <-
  lmer(happiness ~ 
         trial * condition * image * qulty_feel_var.c +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# inspect results
anova(models[["secondary"]][["feel.rating"]])
```

Look at facial feedback task-specific moderating effects
```{r}
# facial mimicry
m <- lmer(happiness ~ 
            trial * image * qulty_feel_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "mimicry")

m %>% anova()
m %>% summary()
m %>% confint()

# voluntary facial action task
m <- lmer(happiness ~ 
            trial * image * qulty_feel_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "directd")

m %>% anova()
m %>% summary()
m %>% confint()

# pen-in-mouth
m <- lmer(happiness ~ 
            trial * image * qulty_feel_var.c +
            (1 | lab) + 
            (1 | ResponseId),
          data = DF.l,
          subset = condition == "pentask")

m %>% anova()
m %>% summary()
m %>% confint()

rm(m)
```

Examine how much genuineness is required for a significant facial feedback effect
```{r}
# fit simpler model without centered variable for ease of interpretation
tmp <- lmer(happiness ~ 
              trial * condition * qulty_feel_var +
         (1 | lab) + 
         (1 | ResponseId),
       data = DF.l)

# 2 is when it switches over (for all conditions)
lapply(X = c(1 : 7), 
       function(x){
         emmeans(tmp,
                 pairwise ~ trial | condition,
                 at = list(qulty_feel_var = x))
         }
       )

# delete vestigial
rm(tmp)
```

##### Awareness
Test whether awareness moderates facial feedback effects
```{r}
# fit model
models[["secondary"]][["awareness"]] <- 
  lmer(happiness ~ 
         trial * condition * image * awareness.c +
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l)

# inspect results
models[["secondary"]][["awareness"]] %>% anova()

models[["secondary"]][["awareness"]] %>% summary()

models[["secondary"]][["awareness"]] %>% confint()

```

Test whether certain facial feedback tasks lead to higher levels of awareness than others
```{r}
# fit model
models[["secondary"]][["awareness.diff"]] <-
  lmer(awareness ~ condition + image + 
         (1 | lab),
       data = DF.w)

# inspect results
anova(models[["secondary"]][["awareness.diff"]])

emmeans(models[["secondary"]][["awareness.diff"]], 
        pairwise ~ condition,
        adjust = "none")

DF.w %>% 
  group_by(condition) %>% 
  summarise(m.awa = mean(awareness,
                         na.rm = T),
            sd.awa = sd(awareness,
                        na.rm = T))
```


##### Body awareness
```{r}
# fit model
models[["secondary"]][["body.aware"]] <- 
  lmer(happiness ~ 
         trial * condition * image *  indiv_body +
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l)

# inspect results
models[["secondary"]][["body.aware"]] %>% anova()
models[["secondary"]][["body.aware"]] %>% summary()
models[["secondary"]][["body.aware"]] %>% confint()

```

### Exploratory Analyses
#### Liking reports
Fit model and inspect results
```{r}
# fit model
models[["exploratory"]][["liking"]] <-
  lmer(tsk ~ trial * condition +
         (1 | lab) +
         (1 | ResponseId),
       data = DF.l.full.inc)

# inspect results
anova(models[["exploratory"]][["liking"]])

joint_tests(models[["exploratory"]][["liking"]], 
            by = "condition",
            lmerTest.limit = 3008)

emmeans(models[["exploratory"]][["liking"]], 
        pairwise ~ trial | condition,
        adjust = "none")

# descriptives
DF.l.full.inc %>% 
  group_by(condition, trial) %>% 
  summarise(m = mean(happiness),
            sd = sd(happiness))

DF.l.full.inc %>% 
  group_by(condition, image, trial) %>% 
  summarise(m = mean(happiness),
            sd = sd(happiness))
```

#### Model with anxiety
```{r}
m <- 
  lmer(happiness ~ trial * image * condition + anxiety +
         (1 | ResponseId) +
         (1 | lab),
       data = DF.l.inc)
    
summary(m) 
confint(m)
anova(m)

joint_tests(m,
            by = "condition",
            lmerTest.limit = 9999)
```

#### Primary analyses excluding anxious participants
Filter data, fit model, inspect results
```{r}
# filter data
DF.inc.no.anx <- DF.l.inc %>% 
  filter(anxiety == 1)

# sample size
DF.inc.no.anx$ResponseId %>% unique %>% length()

# fit model
models[["exploratory"]][["no.anx"]] <- 
  lmer(happiness ~ trial * image * condition +
         (1 | ResponseId) +
         (1 | lab),
       data = DF.inc.no.anx)

# inspect results
anova(models[["exploratory"]][["no.anx"]])

joint_tests(models[["exploratory"]][["no.anx"]],
            by = "condition",
            lmerTest.limit = 9999)

# delete vistigial 
rm(DF.inc.no.anx)
```