---
title: 'Data Visualization Code for the Many Smiles Collaboration'
editor_options:
  chunk_output_type: console
---
## Setup R environment
```{r message = FALSE, results = "hide"}
# clear environment
rm(list = ls())

# install (if necessary) and load packages
  # function written by stevenworthington 
  Ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, 'Package'])]
      
      if (length(new.pkg)) 
          install.packages(new.pkg, dependencies = TRUE)
      
      sapply(pkg, require, character.only = TRUE)
  }

  # vector of necessary packages
  packages <- c('tidyverse', 'ggplot2', 'ggtext', 'metafor')
  
  # using vector of packages, call ipak function
  Ipak(packages)
  
  # delete vestigial
  rm(packages, Ipak)

# turn scientific notation off
options(scipen = 999)

# allow for Type III Sums of Square
options(contrasts = c('contr.sum', 'contr.poly'))

# set plotting options 
theme_set(theme_classic() +
          theme(strip.background = element_rect(fill = "gray35"),
                strip.text =element_text(colour = "white"),
                panel.border = element_blank(),
                legend.position = "none"
                )
          )
```

## Open data
```{r}
DF.w <- readRDS("data/DF.w.rds")
DF.l.full <- readRDS("data/DF.l.full.rds")
DF.l <- readRDS("data/DF.l.rds")
DF.l.inc <- readRDS("data/DF.l.inc.rds")
```

## Recode labels
DF.l
```{r}
DF.l <- DF.l %>%  
  mutate(trial = factor(trial,
                        levels = c("happy",
                                   "neutr",
                                   "fil.1",
                                   "fil.4")),
         trial = recode(trial,
                        fil.1 = "filler 1",
                        happy = "happy",
                        neutr = "neutral",
                        fil.4 = "filler 2"),
         condition = factor(condition,
                            levels = c("mimicry",
                                       "directd",
                                       "pentask")),
         condition = recode(condition,
                            directd = "voluntary facial action",
                            mimicry = "facial mimicry",
                            pentask = "pen-in-mouth"),
         image = recode(image,
                        absentt = "positive stimuli absent",
                        present = "positive stimuli present")
         )
```

DF.l.full
```{r}
DF.l.full <- DF.l.full %>%  
  mutate(trial = factor(trial,
                        levels = c("happy",
                                   "neutr",
                                   "fil.1",
                                   "fil.4")),
         trial = recode(trial,
                        fil.1 = "filler 1",
                        happy = "happy",
                        neutr = "neutral",
                        fil.4 = "filler 2"),
         condition = factor(condition,
                            levels = c("mimicry",
                                       "directd",
                                       "pentask")),
         condition = recode(condition,
                            directd = "voluntary facial action",
                            mimicry = "facial mimicry",
                            pentask = "pen-in-mouth"),
         image = recode(image,
                        absentt = "positive stimuli absent",
                        present = "positive stimuli present")
         )
```

DF.l.inc
```{r}
DF.l.inc <- DF.l.inc %>%  
  mutate(trial = factor(trial,
                        levels = c("happy",
                                   "neutr",
                                   "fil.1",
                                   "fil.4")),
         trial = recode(trial,
                        fil.1 = "filler 1",
                        happy = "happy",
                        neutr = "neutral",
                        fil.4 = "filler 2"),
         condition = factor(condition,
                            levels = c("mimicry",
                                       "directd",
                                       "pentask")),
         condition = recode(condition,
                            directd = "voluntary facial action",
                            mimicry = "facial mimicry",
                            pentask = "pen-in-mouth"),
         image = recode(image,
                        absentt = "positive stimuli absent",
                        present = "positive stimuli present")
         )
```

## Figure 2
Prep dataframe
```{r}
f2.DF <- DF.l %>% 
  # select relevant variables
  select(ResponseId, trial, condition, 
         qulty_rate_var, qulty_feel_var, qulty_smlr_var) %>% 
  
  # pivot longer so that there is one row for each moderator
  pivot_longer(cols = c(qulty_rate_var, 
                        qulty_smlr_var,
                        qulty_feel_var),
               names_to = "qual.ind") %>% 
  
  # delete duplicate set of observations in the neutral trial
  filter(trial == "happy") %>% 
  
  # relevel factors 
  mutate(qual.ind = factor(qual.ind,
                           levels = c("qulty_rate_var",
                                      "qulty_feel_var",
                                      "qulty_smlr_var")),
         qual.ind = recode(qual.ind,
                           qulty_rate_var = "compliance",
                           qulty_feel_var = "genuineness",
                           qulty_smlr_var = "similarity")
         )
```

Get descriptives
```{r}
# m and sd for each quality indicator for each condition 
desc1 <- f2.DF %>% 
  group_by(condition, qual.ind) %>% 
  summarise(m = round(mean(value,
                           na.rm = T),
                      2),
            sd = round(sd(value, na.rm = T),
                       2))

# n for each quality indicator for each condition
desc2 <- f2.DF %>% 
  filter(!is.na(value)) %>% 
  group_by(condition, qual.ind) %>% 
  tally()

# combine
desc <- full_join(desc1, desc2)

rm(desc1, desc2)
```

Plot
```{r}
png(filename = "figures/Figure2.png", 
    units = "in", 
    width = 7, 
    height = 6.5, 
    res = 300)

ggplot(f2.DF,
       aes(x = value)) +
  
  # split plot by condition and moderator
  facet_grid(cols = vars(condition),
             rows = vars(qual.ind),
             scales = "free_y") +
  
  # plot histogram (as percentage)
  geom_histogram(aes(y = stat(width*density)),
                 bins = 7,
                 fill = "gray60") +
  
  # add bin-specific percentage counts to histogram
  stat_bin(aes(y = stat(width*density),
               label = 
                 paste0((round(stat(width*density),
                               2) * 100),
                        "%")), 
           geom = "text",
           bins = 7,
           size = 2,
           vjust = -.21) +
  
  # paste descriptive statistics to left of histogram
  geom_text(data = desc,
            aes(label = paste0("n = ", n,
                               "\n",
                               "M = ", m,
                               "\n",
                               "SD = ", sd)),
            x = -1.25,
            y = Inf,
            size = 2,
            hjust = 0,
            vjust = 1.25) +
  
  # fix scales
  scale_x_continuous(name = "Self-reported rating",
                     breaks = c(1, 3, 5, 7),
                     expand = expand_scale(mult = c(.30, .01))) +
  scale_y_continuous(expand = expand_scale(mult = c(0, .14)),
                     name = "Percent",
                     labels = scales::percent_format())

dev.off()

rm(f2.DF, desc)
```
  
## Figure2b
Prep dataframe
```{r}
f2b.DF <- DF.l.inc %>% 
  # select relevant variables
  select(ResponseId, trial, condition, 
         qulty_rate_var, qulty_feel_var, qulty_smlr_var) %>% 
  
  # pivot longer so that there is one row for each moderator
  pivot_longer(cols = c(qulty_rate_var, 
                        qulty_smlr_var,
                        qulty_feel_var),
               names_to = "qual.ind") %>% 
  
  # delete duplicate set of observations in the neutral trial
  filter(trial == "happy") %>% 
  
  # relevel factors 
  mutate(qual.ind = factor(qual.ind,
                           levels = c("qulty_rate_var",
                                      "qulty_feel_var",
                                      "qulty_smlr_var")),
         qual.ind = recode(qual.ind,
                           qulty_rate_var = "compliance",
                           qulty_feel_var = "genuineness",
                           qulty_smlr_var = "similarity")
         )
```

Get descriptives
```{r}
# m and sd for each quality indicator for each condition 
desc1 <- f2b.DF %>% 
  group_by(condition, qual.ind) %>% 
  summarise(m = round(mean(value,
                           na.rm = T),
                      2),
            sd = round(sd(value, na.rm = T),
                       2))

# n for each quality indicator for each condition
desc2 <- f2b.DF %>% 
  filter(!is.na(value)) %>% 
  group_by(condition, qual.ind) %>% 
  tally()

# combine
desc <- full_join(desc1, desc2)

rm(desc1, desc2)
```

Plot
```{r}
png(filename = "figures/Figure2b.png", 
    units = "in", 
    width = 7, 
    height = 6.5, 
    res = 300)

ggplot(f2b.DF,
       aes(x = value)) +
  
  # split plot by condition and moderator
  facet_grid(cols = vars(condition),
             rows = vars(qual.ind),
             scales = "free_y") +
  
  # plot histogram (as percentage)
  geom_histogram(aes(y = stat(width*density)),
                 bins = 7,
                 fill = "gray60") +
  
  # add bin-specific percentage counts to histogram
  stat_bin(aes(y = stat(width*density),
               label = 
                 paste0((round(stat(width*density),
                               2) * 100),
                        "%")), 
           geom = "text",
           bins = 7,
           size = 2,
           vjust = -.21) +
  
  # paste descriptive statistics to left of histogram
  geom_text(data = desc,
            aes(label = paste0("n = ", n,
                               "\n",
                               "M = ", m,
                               "\n",
                               "SD = ", sd)),
            x = -1.25,
            y = Inf,
            size = 2,
            hjust = 0,
            vjust = 1.25) +
  
  # fix scales
  scale_x_continuous(name = "Self-reported rating",
                     breaks = c(1, 3, 5, 7),
                     expand = expand_scale(mult = c(.30, .01))) +
  scale_y_continuous(expand = expand_scale(mult = c(0, .14)),
                     name = "Percent",
                     labels = scales::percent_format())

dev.off()

rm(f2b.DF, desc)
```

## Figure 3
Prep dataframe
```{r}
f3.DF <- DF.l.inc %>% 
  select(ResponseId, condition, image, trial, happiness) %>% 
  pivot_wider(names_from = "trial",
              values_from = "happiness") %>% 
  rowwise() %>% 
  mutate(happiness.avg = mean(c(happy, neutral))) %>% 
  ungroup()
```

Descriptives
```{r}
desc <- f3.DF %>% 
  group_by(image, condition) %>% 
  summarise(n = n(),
            m = round(mean(happiness.avg),
                      2),
            sd = round(sd(happiness.avg),
                       2))
```

Plot
```{r}
png(
  filename = "figures/Figure3.png",
  units = "in",
  width = 7,
  height = 6.5,
  res = 300
)

ggplot(f3.DF, 
       aes(x = image, 
           y = happiness.avg)) +
  facet_grid(cols = vars(condition)) +
  geom_jitter(width = .1, 
              alpha = .07,
              colour = "dark grey") +
  geom_boxplot(colour = 'dark grey',
               fill = NA,
               outlier.shape = NA) +
  stat_summary(colour = "#3366FF", 
               size = .5,
               fun = "mean") +
  labs(y = "Self-reported happiness", 
       x = "Stimuli Presence") +
  
  # add task-specific M's, SDs,
  geom_text(data = desc,
            aes(label = paste0("n = ", n,
                               "\n", 
                               "M = ", m,
                               "\n",
                               "SD = ", sd)),
            y = 7.3,
            size = 2) +
  scale_y_continuous(
    breaks = c(1, 3, 5, 7)) +
  # adjust scales
  scale_y_continuous(
    breaks = c(1, 3, 5, 7),
    expand = expand_scale(mult = c(0, .1))) +
  
  scale_x_discrete(labels = c("absent", "present"))

dev.off()

rm(desc, f3.DF)
```

## Figure 4
Prep dataframe
```{r}
f4.DF <- DF.l.full %>%
  
  # apply inclusion criteria
  filter(inc == 1,
         inc.awa == 1)
```

Descriptives
```{r}
desc1 <- f4.DF %>% 
  group_by(trial, condition, image) %>% 
  summarise(m = round(mean(happiness),
                      2),
            sd = round(sd(happiness),
                       2))

desc2 <- f4.DF %>% 
  group_by(condition, image) %>%
  summarise(n = length(unique(ResponseId)))

desc <- full_join(desc1, desc2)

rm(desc1, desc2)
```

Make Figure
```{r}
png(filename = "figures/Figure4.png", 
    units = "in", 
    width = 7, 
    height = 6.5, 
    res = 300)

ggplot(f4.DF, 
       aes(x = trial, 
           y = happiness)) +
  # split plot by image and condition
  facet_grid(rows = vars(image),
             cols = vars(condition)) +
  
  # add jittered raw data
  geom_jitter(width = .1, 
              alpha = .07,
              colour = "dark grey") + 
  
  # connect participants' jittered raw data
  geom_line(alpha = .07, 
            aes(group = ResponseId),
            colour = "dark grey") +
  
  # add summary lines
  stat_summary(geom = "line",
               colour = "#3366FF",
               size = 1,
               aes(group = 1)) +
  
  stat_summary(colour = "#3366FF", 
               size = .5,
               fun = "mean") +
  
  # add task-specific M's and SDs
  geom_text(data = desc,
            aes(label = paste0("M = ", m,
                               "\n",
                               "SD = ", sd)),
            y = Inf,
            size = 2,
            vjust = 2) +
  
  # add condition-specific ns
  geom_text(data = desc,
            aes(label = paste0("n = ", n)),
            x = 2.5,
            y = Inf,
            size = 2,
            vjust = 2) +
  
  # adjust scales
  scale_x_discrete(
    expand = expand_scale(mult = c(.2, .2))) +
  
  scale_y_continuous(
    breaks = c(1, 3, 5, 7),
    expand = expand_scale(mult = c(0, .25))) +
  
  labs(y = "Self-reported happiness", 
     x = "Task")

dev.off()

rm(f4.DF, desc)
```


## Figure 5
Prepare dataframe
```{r}
f5.DF <- DF.l %>% 
  # select relevant variables
  select(ResponseId, trial, condition, 
         happiness, qulty_rate_var, 
         qulty_feel_var, qulty_smlr_var) %>% 
  
  # calculate a difference score between the happy and neutral poses☺
  pivot_wider(names_from = trial,
              values_from = happiness) %>%
  rowwise() %>% 
  mutate(happ.diff = happy - neutral) %>% 
  ungroup() %>% 
  
  # pivot longer so that there is one row for each moderator
  pivot_longer(cols = c(qulty_rate_var, 
                        qulty_smlr_var,
                        qulty_feel_var,
                        ),
               names_to = "mod") %>% 
  
  # relevel factors 
  mutate(mod = factor(mod,
                      levels = c("qulty_rate_var",
                                 "qulty_feel_var",
                                 "qulty_smlr_var")),
         mod = recode(mod,
                      qulty_rate_var = "compliance",
                      qulty_feel_var = "genuineness",
                      qulty_smlr_var = "similarity",))
```

For each task, specify modal response and when estimated effect of facial feedback became significant.

Note: these values are hard-coded, but code that shows how these values were derived is in ManySmiles_DataProcessing.Rmd
```{r}
f5.DF$sig.cross = as.numeric(NA)
f5.DF$mode = as.numeric(NA)

# compliance
f5.DF[f5.DF$condition == "facial mimicry" & 
      f5.DF$mod == "compliance", ]$sig.cross <- 5
f5.DF[f5.DF$condition == "facial mimicry" & 
       f5.DF$mod == "compliance", ]$mode <- 7

f5.DF[f5.DF$condition == "voluntary facial action" & 
      f5.DF$mod == "compliance", ]$sig.cross <- 5
f5.DF[f5.DF$condition == "voluntary facial action" & 
     f5.DF$mod == "compliance", ]$mode <- 7

f5.DF[f5.DF$condition == "pen-in-mouth" & 
      f5.DF$mod == "compliance", ]$sig.cross <- 6
f5.DF[f5.DF$condition == "pen-in-mouth" & 
      f5.DFz$mod == "compliance", ]$mode <- 7

# similarity
f5.DF[f5.DF$condition == "facial mimicry" & 
      f5.DF$mod == "similarity", ]$sig.cross <- 3
f5.DF[f5.DF$condition == "facial mimicry" & 
      f5.DF$mod == "similarity", ]$mode <- 6

f5.DF[f5.DF$condition == "voluntary facial action" & 
      f5.DF$mod == "similarity", ]$sig.cross <- 2
f5.DF[f5.DF$condition == "voluntary facial action" & 
      f5.DF$mod == "similarity", ]$mode <- 7

f5.DF[f5.DF$condition == "pen-in-mouth" & 
      f5.DF$mod == "similarity", ]$sig.cross <- 2
f5.DF[f5.DF$condition == "pen-in-mouth" & 
      f5.DF$mod == "similarity", ]$mode <- 6

# genuineness 
f5.DF[f5.DF$mod == "genuineness", ]$sig.cross <- 2

f5.DF[f5.DF$condition == "facial mimicry" & 
      f5.DF$mod == "genuineness", ]$mode <- 5
f5.DF[f5.DF$condition == "voluntary facial action" & 
      f5.DF$mod == "genuineness", ]$mode <- 5
f5.DF[f5.DF$condition == "pen-in-mouth" & 
      f5.DF$mod == "genuineness", ]$mode <- 1
```

Plot figure
```{r}
png(filename = "figures/Figure5.png", 
    units = "in", 
    height = 7, 
    width = 6.5, 
    res = 300)

ggplot(f5.DF, 
       aes(x = value, 
           y = happ.diff)) +
  facet_grid(cols = vars(condition),
             rows = vars(mod)) +
  geom_rect(aes(xmin = sig.cross - .25,
                xmax = 7.25,
                ymin = -6,
                ymax = 6),
            fill = "lightgreen",
            alpha = .01) +
  geom_rect(aes(xmin = mode - .25,
                xmax = mode + .25,
                ymin = -6,
                ymax = 6),
            fill = NA,
            colour = "black") + 
  geom_jitter(width = .1, 
              alpha = .2,
              colour = "dark grey") +
  geom_smooth(method = 'lm') +
  xlab("Self-reported rating") +
  ylab("Change in self-reported happiness") + 
  scale_x_continuous(
    breaks = c(1, 3, 5, 7))

dev.off()

rm(f5.DF)
```


## Figure 6
Reformat DF.l.inc to make the code a little cleaner
```{r}
DF.l.inc <- DF.l.inc %>%
  mutate(image = recode(image,
                        `positive stimuli absent` = "absentt",
                        `positive stimuli present` = "present")
         )
```


Calculate country-specific effect sizes for facial feedback tasks
```{r}
pose.es.DF <- DF.l.inc %>%
  # pivot data wider
  pivot_wider(names_from = trial,
              values_from = happiness,
              id_cols = c(ResponseId,
                          country,
                          lab,
                          UserLanguage,
                          condition)) %>% 
  
  # calculate difference score
  rowwise() %>% 
  mutate(diff = happy - neutral) %>% 
  
  # for each condition and country, find correlation between two trials and the mean/sd of the difference score
  group_by(condition, country) %>% 
  summarise(n = n(),
            corr = cor(happy, neutral),
            m.diff = mean(diff),
            sd.diff = sd(diff)) %>% 
  ungroup() %>% 
  
  # calculate cohen drm
  # formula: Cooper, Hedges, & Valentine, 2009; p. 229
  rowwise() %>% 
  mutate(d = (m.diff / sd.diff) * 
           sqrt(2 * (1 - corr))) %>% 
  
  # calculate variance of d
  mutate(d.var = ((1 / n) + ((d^2) / (2 * n))) * 
           2 * (1 - corr)) %>% 
  
  # calculate CI of d
  mutate(lb = d - (1.96 * sqrt(d.var)),
         ub = d + (1.96 * sqrt(d.var))) %>% 
  
  # select relevant variables
  select(condition, country, d, d.var, lb, ub)
```

Calculate country-specific effect sizes for image
```{r}
img.es.DF <- DF.l.inc %>% 
  # pivot data wide
  pivot_wider(names_from = trial,
              values_from = happiness,
              id_cols = c(ResponseId,
                          country,
                          image,
                          lab,
                          UserLanguage,
                          condition)) %>% 
  
  # remove pen-in-mouth
  filter(condition != "pentask") %>% 
  
  # calculate happiness mean and sd when images were present vs. absent in each country
  group_by(country, image) %>% 
  summarise(n = n(),
            m = mean(neutral),
            sd = sd(neutral)) %>%
  ungroup() %>% 
  
  # pivot data wider
  pivot_wider(names_from = image,
              values_from = c(n, m, sd)) %>% 
  
  # calculate cohen's drm
  # formula: Cooper, Hedges, & Valentine, 2009; p. 226
  rowwise() %>% 
  mutate(sd.pooled = sqrt((((n_absentt - 1) * (sd_absentt^2)) +
                             ((n_present - 1) * (sd_present^2))) /
                            (n_absentt + n_present - 2))) %>% 
  mutate(d = (m_present - m_absentt) / sd.pooled) %>% 

  # calculate variance of cohen's d
  mutate(d.var = ((n_absentt + n_present) / (n_absentt * n_present)) +
           ((d^2) / (2 * (n_absentt + n_present)))) %>% 
  
  # calculate CI of d
  mutate(lb = d - (1.96 * sqrt(d.var)),
         ub = d + (1.96 * sqrt(d.var))) %>% 
  
  # match formatting with meta.DF
  mutate(condition = "image") %>% 
  select(condition, country, d, d.var, lb, ub)
```

Merge facial feedback and image effect size databases
```{r}
meta.DF <- rbind(pose.es.DF, img.es.DF) %>% 
  as.data.frame()

rm(pose.es.DF, img.es.DF)
```

Fit random effects meta-analyses
```{r}
# overall effect
rma(
  yi = d,
  vi = d.var,
  slab = country,
  data = meta.DF,
  subset = condition != "image"
)

# moderation by facial feedback task
rma(
  yi = d,
  vi = d.var,
  mods = condition,
  slab = country,
  data = meta.DF,
  subset = condition != "image"
)

# facial feedback task meta-analysis
meta.m  <- rma(
  yi = d,
  vi = d.var,
  slab = country,
  data = meta.DF,
  subset = condition == "facial mimicry")

meta.d <- rma(
  yi = d,
  vi = d.var,
  slab = country,
  data = meta.DF,
  subset = condition == "voluntary facial action"
)

meta.p <- rma(
  yi = d,
  vi = d.var,
  slab = country,
  data = meta.DF,
  subset = condition == "pen-in-mouth"
)

# meta-analysis for images
meta.i <- rma(
  yi = d,
  vi = d.var,
  slab = country,
  data = meta.DF,
  subset = condition == "image"
)
```

Add meta-analytic results to dataframe
```{r}
meta.DF <- meta.DF %>% 
  mutate(Q = NA,
         Q.p = NA,
         i2 = NA,
         t2 = NA)

meta.DF <- rbind(
  meta.DF,
  
  # mimicry
  cbind(
    condition = "facial mimicry",
    country = "Overall",
    d = meta.m[["beta"]] %>%
      as.numeric(),
    d.var = meta.m[["se"]] ^ 2,
    lb = meta.m[["ci.lb"]],
    ub = meta.m[["ci.ub"]],
    Q = round(meta.m$QE, 2),
    Q.p = round(meta.m$QEp, 3),
    i2 = round(meta.m$I2, 0),
    t2 = round(meta.m$tau2, 2)
  ),
  
  # directd
  cbind(
    condition = "voluntary facial action",
    country = "Overall",
    d = meta.d[["beta"]] %>%
      as.numeric(),
    d.var = meta.d[["se"]] ^ 2,
    lb = meta.d[["ci.lb"]],
    ub = meta.d[["ci.ub"]],
    Q = round(meta.d$QE, 2),
    Q.p = round(meta.d$QEp, 3),
    i2 = round(meta.d$I2, 0),
    t2 = round(meta.d$tau2, 2)
  ),
  
  # pentask
  cbind(
    condition = "pen-in-mouth",
    country = "Overall",
    d = meta.p[["beta"]] %>%
      as.numeric(),
    d.var = meta.p[["se"]] ^ 2,
    lb = meta.p[["ci.lb"]],
    ub = meta.p[["ci.ub"]],
    Q = round(meta.p$QE, 2),
    Q.p = round(meta.p$QEp, 3),
    i2 = round(meta.p$I2, 0),
    t2 = round(meta.p$tau2, 2)
  ),
  
  # image
  cbind(
    condition = "image",
    country = "Overall",
    d = meta.i[["beta"]] %>%
      as.numeric(),
    d.var = meta.i[["se"]] ^ 2,
    lb = meta.i[["ci.lb"]],
    ub = meta.i[["ci.ub"]],
    Q = round(meta.i$QE, 2),
    Q.p = round(meta.i$QEp, 3),
    i2 = round(meta.i$I2, 0),
    t2 = round(meta.i$tau2, 2)
  )
) %>% as.data.frame()

rm(meta.d, meta.m, meta.p, meta.i)
```

Format dataset
```{r}
meta.DF <- meta.DF %>% 
  mutate(
    # identify which effects are overall vs. country-specific
    overall = if_else(condition = country == "Overall",
                      true = 1, 
                      false = 0),
    
    # order effect sizes by whether they are (a) overall vs. country-specific and then (b) size of the effect
    country = fct_reorder(country,
                          desc(d)),
    country = fct_reorder(country,
                          desc(overall)),
    
    # fix format of numeric variables
    d = as.numeric(d),
    lb = as.numeric(lb),
    ub = as.numeric(ub),
    
    # relevel and recode condition variable
    condition = factor(condition,
                       levels = c("facial mimicry",
                                  "voluntary facial action",
                                  "pen-in-mouth",
                                  "image")),
    condition = recode(condition,
                       image = "exposure to positive images"))
```

Create forest plot
```{r}
png(filename = "figures/Figure6.png", 
    units = "in", 
    width = 9, 
    height = 5.07, 
    res = 300)

ggplot(data = meta.DF, 
       aes(x = country, 
           y = d,
           ymin = lb,
           ymax = ub)) +
  geom_rect(aes(fill = condition),
            xmin = -Inf, xmax = Inf,
            ymin = -Inf, ymax = Inf,
            alpha = 0.3) +
  geom_hline(yintercept = 0, 
             color = "black", 
             linetype = "dashed", 
             alpha = .5) +
  geom_point(aes(shape = as.factor(overall),
                 size = as.factor(overall),
                 colour = as.factor(overall))) +
  geom_errorbar(width = .5,
                aes(colour = as.factor(overall))) +
  scale_shape_manual(values = c(15, 18)) +
  scale_size_manual(values = c(2, 4)) +
  scale_color_manual(values= c("dark grey", 
                               "#3366FF")) +
  scale_fill_manual(values = c("white",
                               "white",
                               "white",
                               "ivory2")) +
  coord_flip() +
  facet_grid(cols = vars(condition)) +
  labs(y = expression(paste("Cohen's ", 
                            italic("d"))
                      ),
       x = "Country") +
  ylim(-1.5, 3) +
  geom_richtext(data = meta.DF[meta.DF$overall == 1, ],
            aes(label = paste0("overall <i>d</i> = ", round(d, 2),
                               " [", round(lb, 2), ", ",
                               round(ub, 2), "]",
                               "<br>",
                               " Q = ", Q, ", 
                               <i>p</i> =", round(as.numeric(Q.p), 2),
                               "<br>",
                               " <i>I<sup>2</sup></i> = ", i2, "%", 
                               ", <i>T<sup>2</sup></i> = ", t2),
                x = 1.18,
                y = .8),
            size = 1.8,
            label.colour = NA,
            fill = NA,
            hjust = 0)

dev.off()

rm(meta.DF)
```
