---
title: 'Data Processing Code for the Many Smiles Collaboration'
editor_options:
  chunk_output_type: console
---
## Setup R environment
```{r message = FALSE, results = "hide"}
# clear environment
rm(list = ls())

# install (if necessary) and load packages
  # function written by stevenworthington 
  Ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, 'Package'])]
      
      if (length(new.pkg)) 
          install.packages(new.pkg, dependencies = TRUE)
      
      sapply(pkg, require, character.only = TRUE)
  }

  # vector of necessary packages
  packages <- c('tidyverse', 'qualtRics', 
                'googlesheets4', 'readxl',
                'psych')
  
  # using vector of packages, call ipak function
  Ipak(packages)
  
  # delete vestigial
  rm(packages, Ipak)

# allow for Type III SS
options(contrasts = c('contr.sum', 'contr.poly'))
```

## Open data via Qualtrics API
Set API credentials
```{r eval = FALSE}
qualtrics_api_credentials(
  api_key = 'Qtd8CzAV5LeEfGyQQiMBpF8YXSq7zHbKF5A0j1Mn', 
  base_url = 'sjc1.qualtrics.com',
  install = TRUE,
  overwrite = TRUE)
```

Load data
```{r}
DF <- all_surveys() %>% 
  fetch_survey(surveyID = 'SV_1MHZifyxXFTQMGp',
               force_request = TRUE,
               label = FALSE,
               convert = FALSE,
               fileEncoding = "UTF-8")
```

## Fix documented issues
Issue Report 1/11/2021 15:27:16
```{r}
DF[DF$ResponseId == 'R_71mBhLa0wTLkE9P', ]$lab <- "USA_02"
DF[DF$ResponseId == 'R_71mBhLa0wTLkE9P', ]$mode <- "online"

DF[DF$ResponseId == 'R_Y5eNgLXGXayulH3', ]$lab <- "USA_02"
DF[DF$ResponseId == 'R_Y5eNgLXGXayulH3', ]$mode <- "online"

DF[DF$ResponseId == 'R_336V86Y5lFAErTD', ]$lab <- "USA_02"
DF[DF$ResponseId == 'R_336V86Y5lFAErTD', ]$mode <- "online"
```

Issue Report 3/10/2021 13:04:13
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_24pYUstgkOOGxLs",
         ResponseId != "R_ZrG6EKkXCgsUcCd",
         ResponseId != "R_Y4eZs4E4YuVAZfH",
         ResponseId != "R_3nTmxu3vObT2JHh",
         ResponseId != "R_3g0zJDrM9ytHC71",
         ResponseId != "R_28Aq1V3WJBwwpNM",
         ResponseId != "R_3lEs4Szd6p5WnkU",
         ResponseId != "R_sALi2EPfHu7xhGp")
```

Issue Report 2/1/2021 11:06:16
```{r}
DF[!is.na(DF$comp_code) & DF$comp_code == 50011, ]$lab <- "GBR_01"
DF[!is.na(DF$comp_code) & DF$comp_code == 50011, ]$mode <- "online"
```

Issue Report 3/10/2021 16:00:55
```{r}
ids <-
  c("R_1GD4F1SkMf9kfej", "R_9Y64npYAReaM2bv", 
    "R_1Dr0VPNxpieom2m", "R_33d5XLn9fbq9xKK",
    "R_25A6NQrZvWRKUL4", "R_2PjsokzhdsD2vZj",
    "R_2Qtk9qpd520bKMP", "R_e38EizEqLMVfA09",
    "R_2BmrrTge0O7l4SU", "R_1jSOkeCyxfswvNN",
    "R_3KrLO7nsoiAFwsL", "R_1ovashQAQ6fDomE",
    "R_1Ej0NXzFob65t2o", "R_NVzxKo4NqK0U7fP",
    "R_3FUqkkW2BKltGmW", "R_1jkPjgj145hnjtV",
    "R_3nIfmyaH4kOeJcB", "R_2WHxeiVG0if6IDO",
    "R_2TFfFcUCVAAsVH7", "R_UEdaTAgiXo7qnbb")

for (i in ids){
  DF[DF$ResponseId == i, ]$lab <- "AUS_01"
  DF[DF$ResponseId == i, ]$mode <- "online"
}

rm(i, ids)
```

Issue Report 3/11/2021 12:27:11
```{r}
DF <- DF %>% 
  filter(ResponseId != 'R_1FQAgvtC22eIEmo')
```

Issue Report 4/13/2021 12:32:27
```{r}
DF <- DF %>% 
  filter(ResponseId != 'R_3ff7VJO1aIUfhrY',
         ResponseId != 'R_3J7VlYAposubTqQ',
         ResponseId != 'R_2as3VAy174nEEUE',
         ResponseId != 'R_25NJqFnThS6T9gw')
```

Issue Report 4/19/2021 16:10:38
```{r}
DF <- DF %>% 
  filter(ResponseId != 'R_3PSwb7kaUELPdOQ',
         ResponseId != 'R_2TTWPmgmGBzJo4u',
         ResponseId != 'R_31aRdUehVCYMrRo',
         ResponseId != 'R_1QDTXhBqAGOgMu0',
         ResponseId != 'R_22ulZEcvoGxSUAk')
```

Issue Report 5/3/2021 13:42:19
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_1eK3FNOOZQZHov4",
         ResponseId != "R_1giES2oovR2sJGo",
         ResponseId != "R_1gvdVKTh2Q7IYvw",
         ResponseId != "R_1OGBoYWh7Wy6t90",
         ResponseId != "R_1OHttohbOonQR3f",
         ResponseId != "R_1rGsxNubojx9p5s",
         ResponseId != "R_2ab26zkYpicljIL",
         ResponseId != "R_2ariEOYgWmeUb3D",
         ResponseId != "R_2CJ3p00nKpIVD6p",
         ResponseId != "R_2CJ3p00nKpIVD6p",
         ResponseId != "R_2cnjhdhKXJO2EjU",
         ResponseId != "R_2RZVdR1OUjWVKZM",
         ResponseId != "R_2SxiNXD4kHPVdCK",
         ResponseId != "R_2uwvT1YvWYxaCaN",
         ResponseId != "R_2vc6Snh5gCe7RYs",
         ResponseId != "R_2VQnnlaCBBz2ZOB",
         ResponseId != "R_30wPj1MIb5h4Yx7",
         ResponseId != "R_3DvATATzYPMh0MA",
         ResponseId != "R_3inei4TekzBMBgC",
         ResponseId != "R_3lAELDkUxJar9qx",
         ResponseId != "R_3p9D1AsSzStrMbz",
         ResponseId != "R_3szfC3fIUH6SDmw",
         ResponseId != "R_6fbnBLbFxHrdaYp",
         ResponseId != "R_74cC2EOdWmFJPdn",
         ResponseId != "R_cUtMWAOJRPYKIBr",
         ResponseId != "R_d0Yqdl0vmv56Y5b",
         ResponseId != "R_QnxxXHNugmQ4UtH",
         ResponseId != "R_RVKns4AP1CXaknL",
         ResponseId != "R_Un0uPQitlSLvnFL",
         ResponseId != "R_vCs5PjQe7Zw2xsl",
         ResponseId != "R_W3eg3lgdvdl5n5n",
         ResponseId != "R_w6562GdZqsX7WPT",
         ResponseId != "R_xhAWlsmsZ5tj6qR",
         ResponseId != "R_yqoCD9H8bUBnJCN",
         ResponseId != "R_Z42JMemfxctMx1v",
         ResponseId != "R_zTMyGcAsKIAHvBn")
```  

Issue Report 5/3/2021 15:45:45
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_2fHgqY784oIsl23",
         ResponseId != "R_2anPJwvrQ1xvaQw",
         ResponseId != "R_1rCuopgnEYbhZbe",
         ResponseId != "R_1Cg0Ut7JsIUCTLt",
         ResponseId != "R_1gu4j0wbEEu5NpB",
         ResponseId != "R_2Vm8k8lidsF4kK7")
```

Issue Report 5/4/2021 7:15:04
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_yyJM8Jbrnu9UcwN")
```

Issue Report 5/4/2021 7:35:25
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_1JJH6cMwmsFEs4N")
```

Issue Report 5/10/2021 9:27:17
```{r}
DF <- DF %>% 
  filter(ResponseId != "R_1Ok4MouIQIvgj8Q",
         ResponseId != "R_Y4Fp9VO9dCrgaFH")
```

## Prep data review and coding sheets
Note: this code is set to eval = FALSE because it is only used when Nicholas needs to prep a data review or coding sheet

Identify lab
```{r eval = FALSE}
site <- "CHE_01"
```

Create review sheet
```{r eval = FALSE}
review <- DF %>% 
  # select site-specific data
  filter(as.character(lab) == site) %>% 
  
  # select relevant variables
  select(DistributionChannel, StartDate, Progress,
         aware_intv_q01, aware_intv_q03,
         quali_chek_que) %>% 
  
  # create column for identifying issues
  mutate(Participant.Miscategorized = "",
         Note = "") %>% 
  
  # rename columns
  rename(DataClassification = DistributionChannel) %>% 
   
  # sort
  arrange(desc(DataClassification),
          StartDate)

# rename levels of Test
review[review$DataClassification == "preview", ]$DataClassification <- "test"
review[review$DataClassification == "anonymous", ]$DataClassification <- "real"
  
gs4_create(paste0(site, "_DataClassification"),
           sheets = review)

rm(review)
```

Create coding sheet
```{r eval = FALSE}
coding <- DF %>% 
  # select site-specific non-test data
  filter(as.character(lab) == site,
         DistributionChannel != 'preview') %>% 
  
  # randomize order
  mutate(rand = runif(n = nrow(.))) %>% 
  arrange(rand) %>% 
  
  # create blank coding columns
  mutate(Awareness = "",
         Distraction = "") %>% 
  
  # select relevant variables
  select(ResponseId, 
         aware_intv_q01, aware_intv_q02, aware_intv_q03, 
         Awareness, quali_chek_que, Distraction)

gs4_create(paste0(site, "_coder1"),
           sheets = coding)

rm(coding)
```

## Open and merge open-ended coding data with Qualtrics data
```{r}
# create blank dataframe for coding data
coding.DF <- data.frame(Awareness1 = numeric(),
                        Distraction1 = numeric(),
                        Awareness2 = numeric(),
                        Distraction2 = numeric())

# create list of countries with completed open-ended data
countries <- c("USA_02", "NOR_01", "ESP_01", 
               "FRA_01", "JPN_01", "HUN_01",
               "ISR_01")

# append coding data to coding.DF
for (c in countries){
  # coder 1
  ## open coding file
  coder1 <- 
    read_excel(path = 
                 paste0("data/coding/",
                        c,
                        "_coder1.xlsx"),
               col_types = 
                 c("text", 
                   "skip", "skip", "skip",
                   "numeric",
                   "skip",
                   "numeric"),
               na = c("N/A", "NA")) %>% 
  
  ## append coder number to columns
  rename_at(.vars = vars(Awareness, Distraction), 
            function(x) paste0(x,
                               1))
  
  # coder 2
  ## open coding file
  coder2 <- 
    read_excel(path = 
                 paste0("data/coding/",
                        c,
                        "_coder2.xlsx"),
               col_types = 
                 c("text", 
                   "skip", "skip", "skip",
                   "numeric",
                   "skip",
                   "numeric"),
               na = c("N/A", "NA")) %>% 
  
  ## append coder number to columns
  rename_at(.vars = vars(Awareness, Distraction), 
            function(x) paste0(x,
                               2))
  
  # merge two coders' data
  coder <- full_join(x = coder1, y = coder2,
                     by = 'ResponseId')
  
  # merge coding data with coding dataframe
  coding.DF <- rbind(coding.DF,
                     coder)
}

# merge coding.DF data with main dataframe
DF <- full_join(x = DF, y = coding.DF, 
                by = "ResponseId")

# delete vestigial
rm(coder, coder1, coder2, coding.DF, c, countries)
```

## Clean data
Remove test data and select relevant variables
```{r}
DF <- DF %>% 
  # remove test data
  filter(DistributionChannel != 'preview') %>% 
  
  # remove incomplete observations
  filter(Progress > 90) %>% 
  
  # select relevant variables
  select(
    # subject id and condition identifiers 
    ResponseId, lab, mode, UserLanguage, condition, image,
    
    # filler 1 responses
    fil.1_emot_ang : fil.1_emot_wor,
    fil.1_diff_dq1, fil.1_like_tsk,
    
    # neutral trial responses
    neutr_emot_ang : neutr_emot_wor,
    neutr_diff_dq1, neutr_like_tsk,
    
    # happy trial responses
    happy_emot_ang : happy_emot_wor,
    happy_diff_dq1, happy_like_tsk,
    
    # filler 4 responses
    fil.4_emot_ang : fil.4_emot_wor,
    fil.4_diff_dq1, fil.4_like_tsk,
    
    # individual differences
    indiv_gend_var, indiv_agee_var,
    indiv_body_001 : indiv_body_018,
    
    # quality control variables
    Progress, `Duration (in seconds)`,
    `metaa_data_que_Operating System`,
    
    intro_filt_1 : intro_filt_3, 
    
    fil.1_math_mq1, neutr_math_mq1, 
    happy_math_mq1, fil.4_math_mq1, 
    
    neutr_diff_att, happy_diff_att,
    
    qulty_rate_var, qulty_feel_var, 
    descr_smlr_tx1, qulty_smlr_var,
    Awareness1 : Distraction2
    )
```

Calculate awareness and distraction scores 
```{r}
DF <- DF %>% 
  rowwise() %>% 
  mutate(awareness = mean(c(Awareness1,
                            Awareness2)),
         distraction = mean(c(Distraction1,
                              Distraction2)))

# examine IRR of awareness and distraction scores
DF %>% 
  select(Awareness1, Awareness2) %>% 
  alpha()

DF %>% 
  select(Distraction1, Distraction2) %>% 
  alpha()

# delete vestigial 
DF <- DF %>% 
  select(-c(Awareness1 : Distraction2))
```

Code for whether participants meet inclusion criteria
- Failed attention checks
- Indicated that they did not follow pose expression
- Indicated that their expression did not match the image of an actor completing the task correctly
- Did not complete study on desktop computer or laptop (will want to check that OS's are correct)
- Awareness of hypothesis
- Indicated that they were very distracted

```{r}
DF <- DF %>% 
  # specific inclusion criterion
  mutate(
         # attention check items
         inc.att = if_else(condition = neutr_diff_att == 7 &
                             happy_diff_att == 7,
                           true = 1,
                           false = 0),
         
         # participant ratings of degree to which they followed instructions 
         inc.fol = if_else(condition = qulty_rate_var > 1,
                           true = 1,
                           false = 0),
         
         # participant ratings of degree to which posed expressions matched image of actor
         inc.mat = if_else(condition = 
                             is.na(qulty_smlr_var) | 
                             qulty_smlr_var > 1,
                           true = 1,
                           false = 0),
         
         # browser
         inc.dev = if_else(condition = 
                             `metaa_data_que_Operating System` == "Android 7.0" |
                             `metaa_data_que_Operating System` == "Android 8.0.0" |
                             `metaa_data_que_Operating System` == "Android 9" |
                             `metaa_data_que_Operating System` == "Android 9" |
                             `metaa_data_que_Operating System` == "iPhone" |
                             `metaa_data_que_Operating System` == "iPad",
                           true = 0,
                           false = 1)) %>% 
  
  # overall inclusion criteria
  mutate(inc = if_else(condition = 
                         inc.att == 0 |
                         inc.fol == 0 |
                         inc.mat == 0 | 
                         inc.dev == 0 |
                         awareness > 1 |
                         distraction > 5,
                       true = 0,
                       false = 1))

# delete vestigial columns
DF <- DF %>% 
  select(-c(neutr_diff_att, happy_diff_att,
            `metaa_data_que_Operating System`))
```

Mean-center continuous variables that will be used in later moderation analyses
```{r}
DF$qulty_rate_var <- scale(x = DF$qulty_rate_var,
                           center = T,
                           scale = F)

DF$awareness <- scale(x = DF$awareness,
                      center = T,
                      scale = F)
```

## Create long-format dataframe
```{r}
DF.l <- DF %>%
  pivot_longer(cols = c(neutr_emot_ang : neutr_like_tsk, # neutral trial responses
                        happy_emot_ang : happy_like_tsk, # happy trial responses
                        fil.1_emot_ang : fil.1_like_tsk, # filler 1 trial responses
                        fil.4_emot_ang : fil.4_like_tsk), # filler 4 trial responses
               names_to = "dv",
               values_to = "value") %>% 
  
  separate(col = "dv", into = c("trial", "outcome"),
           sep = "_...._") %>% 
  
  pivot_wider(names_from = "outcome",
              values_from = "value") %>% 
  
  arrange(ResponseId, trial)
```

#### Calculate scales
```{r}
DF.l <- DF.l %>% 
  rowwise() %>% 
  # happiness items
  mutate(happiness = mean(c(enj, hap, 
                            lke, sat))) %>% 
  
  # anxiety items
  mutate(anxiety = mean(c(nrv, wor))) %>% 
  
  # anger itmes
  rename(anger = ang) %>% 
         
  # body awareness
    ## reverse score item 10
    mutate(indiv_body_010 = (8 - indiv_body_010)) %>% 
    
    ## average all items
    mutate(indiv_body = mean(c(indiv_body_001, indiv_body_002,
                               indiv_body_003, indiv_body_004,
                               indiv_body_005, indiv_body_006,
                               indiv_body_007, indiv_body_008,
                               indiv_body_009, indiv_body_010,
                               indiv_body_011, indiv_body_012,
                               indiv_body_013, indiv_body_014,
                               indiv_body_015, indiv_body_016,
                               indiv_body_017, indiv_body_018))
          ) %>% 
  ungroup()
```

#### Sort columns and rows to improve readability
```{r}
DF.l <- DF.l %>%
  # Sort columns
  select( 
    # subject id and condition identifiers 
    ResponseId, lab, 
    mode, condition, image, trial,
    
    # emotion ratings
    happiness, enj, hap, lke, sat, # happiness ratings
    anxiety, nrv, wor, # anxiety ratings
    anger, # anger ratings
    lke, # liking ratings
    
    # inclusion criteria
    awareness, distraction, inc.att : inc,
    
    # quality items
    qulty_rate_var, qulty_feel_var, qulty_smlr_var,
    
    # demographics
    indiv_gend_var, indiv_agee_var, indiv_body, inc
    )
```

Delete original dataframe
```{r}
rm(DF)
```

### Limit long format to only the critical trials
```{r}
DF.l.full <- DF.l

DF.l <- DF.l %>%
  filter(trial == "happy" |
         trial == "neutr")
```

## Convert subject id, condition, study, and trial to factors
```{r}
DF.l$ResponseId <- as.factor(DF.l$ResponseId)
DF.l$lab <- as.factor(DF.l$lab)
DF.l$condition <- as.factor(DF.l$condition) 
DF.l$image <- as.factor(DF.l$image)
DF.l$trial <- as.factor(DF.l$trial)

DF.l.full$ResponseId <- as.factor(DF.l.full$ResponseId)
DF.l.full$lab <- as.factor(DF.l.full$lab)
DF.l.full$condition <- as.factor(DF.l.full$condition) 
DF.l.full$image <- as.factor(DF.l.full$image)
DF.l.full$trial <- as.factor(DF.l.full$trial)
```

```{r}
write_rds(DF.l, "data/DF.l.rds")
write_rds(DF.l.full, "data/DF.l.full.rds")
```

```{r}

```
